\item $\exists x \in A$, $\PPP{x}$.
\item $\exists x \in A$ such that $\PPP{x}$.
\item $\exists x \in A$ s.t. $\PPP{x}$.
\item $x\in A$が存在し, $\PPP{x}$.
\item $x\in A$が存在し, $\PPP{x}$が成り立つ.
\item $x\in A$が存在し, 次が成り立つ: $\PPP{x}$.
\item $x\in A$が存在し, その$x$に対し$\PPP{x}$.
\item $x\in A$が存在し, その$x$に対し$\PPP{x}$が成り立つ.
\item $x\in A$が存在し, その$x$に対し次が成り立つ: $\PPP{x}$.
\item ある$x\in A$が存在し, $\PPP{x}$.
\item ある$x\in A$が存在し, $\PPP{x}$が成り立つ.
\item ある$x\in A$が存在し, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$に対して, $\PPP{x}$.
\item ある$x\in A$に対して, $\PPP{x}$が成り立つ.
\item ある$x\in A$に対して, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$について, $\PPP{x}$.
\item ある$x\in A$について, $\PPP{x}$が成り立つ.
\item ある$x\in A$について, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$において, $\PPP{x}$.
\item ある$x\in A$において, $\PPP{x}$が成り立つ.
\item ある$x\in A$において, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$で, $\PPP{x}$.
\item ある$x\in A$で, $\PPP{x}$が成り立つ.
\item ある$x\in A$で, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$では, $\PPP{x}$.
\item ある$x\in A$では, $\PPP{x}$が成り立つ.
\item ある$x\in A$では, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$が, $\PPP{x}$を満たす.
\item ある$x\in A$が, 次を満たす: $\PPP{x}$.
\item 次の条件を満たす$x\in A$が存在する: $\PPP{x}$.
\item ある$x\in A$がとれて, $\PPP{x}$.
\item ある$x\in A$がとれて, $\PPP{x}$が成り立つ.
\item ある$x\in A$がとれて, 次が成り立つ: $\PPP{x}$.
\item ある$x\in A$がとれて, その$x$に対し$\PPP{x}$.
\item ある$x\in A$がとれて, その$x$に対し$\PPP{x}$が成り立つ.
\item ある$x\in A$がとれて, その$x$に対し次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$が存在し, $\PPP{x}$.
\item 適当な$x\in A$が存在し, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$が存在し, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$に対して, $\PPP{x}$.
\item 適当な$x\in A$に対して, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$に対して, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$について, $\PPP{x}$.
\item 適当な$x\in A$について, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$について, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$において, $\PPP{x}$.
\item 適当な$x\in A$において, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$において, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$で, $\PPP{x}$.
\item 適当な$x\in A$で, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$で, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$では, $\PPP{x}$.
\item 適当な$x\in A$では, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$では, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$が, $\PPP{x}$を満たす.
\item 適当な$x\in A$が, 次を満たす: $\PPP{x}$.
\item 適当な$x\in A$がとれて, $\PPP{x}$.
\item 適当な$x\in A$がとれて, $\PPP{x}$が成り立つ.
\item 適当な$x\in A$がとれて, 次が成り立つ: $\PPP{x}$.
\item 適当な$x\in A$がとれて, その$x$に対し$\PPP{x}$.
\item 適当な$x\in A$がとれて, その$x$に対し$\PPP{x}$が成り立つ.
\item 適当な$x\in A$がとれて, その$x$に対し次が成り立つ: $\PPP{x}$.
