\item $x\in A$となるのは, $\PPP{x}$のときのみ.
\item $x\in A$となるのは, $\PPP{x}$となるときのみ.
\item $x\in A$となるのは, $\PPP{x}$を満たすときのみ.
\item $x\in A$となるのは, $\PPP{x}$が成り立つときのみ.
\item $x\in A$となるのは, $\PPP{x}$のときに限る.
\item $x\in A$となるのは, $\PPP{x}$となるときに限る.
\item $x\in A$となるのは, $\PPP{x}$を満たすときに限る.
\item $x\in A$となるのは, $\PPP{x}$が成り立つときに限る.
\item $x\in A$を満たすのは, $\PPP{x}$のときのみ.
\item $x\in A$を満たすのは, $\PPP{x}$となるときのみ.
\item $x\in A$を満たすのは, $\PPP{x}$を満たすときのみ.
\item $x\in A$を満たすのは, $\PPP{x}$が成り立つときのみ.
\item $x\in A$を満たすのは, $\PPP{x}$のときに限る.
\item $x\in A$を満たすのは, $\PPP{x}$となるときに限る.
\item $x\in A$を満たすのは, $\PPP{x}$を満たすときに限る.
\item $x\in A$を満たすのは, $\PPP{x}$が成り立つときに限る.
\item $x\in A$が成り立つのは, $\PPP{x}$のときのみ.
\item $x\in A$が成り立つのは, $\PPP{x}$となるときのみ.
\item $x\in A$が成り立つのは, $\PPP{x}$を満たすときのみ.
\item $x\in A$が成り立つのは, $\PPP{x}$が成り立つときのみ.
\item $x\in A$が成り立つのは, $\PPP{x}$のときに限る.
\item $x\in A$が成り立つのは, $\PPP{x}$となるときに限る.
\item $x\in A$が成り立つのは, $\PPP{x}$を満たすときに限る.
\item $x\in A$が成り立つのは, $\PPP{x}$が成り立つときに限る.
\item $\PPP{x}$に限り, $x\in A$.
\item $\PPP{x}$のときに限り, $x\in A$.
\item $\PPP{x}$となるときに限り, $x\in A$.
\item $\PPP{x}$を満たすときに限り, $x\in A$.
\item $\PPP{x}$が成り立つときに限り, $x\in A$.
\item $\PPP{x}$に限り, $x\in A$となる.
\item $\PPP{x}$のときに限り, $x\in A$となる.
\item $\PPP{x}$となるときに限り, $x\in A$となる.
\item $\PPP{x}$を満たすときに限り, $x\in A$となる.
\item $\PPP{x}$が成り立つときに限り, $x\in A$となる.
\item $\PPP{x}$に限り, $x\in A$を満たす.
\item $\PPP{x}$のときに限り, $x\in A$を満たす.
\item $\PPP{x}$となるときに限り, $x\in A$を満たす.
\item $\PPP{x}$を満たすときに限り, $x\in A$を満たす.
\item $\PPP{x}$が成り立つときに限り, $x\in A$を満たす.
\item $\PPP{x}$に限り, $x\in A$が成り立つ.
\item $\PPP{x}$のときに限り, $x\in A$が成り立つ.
\item $\PPP{x}$となるときに限り, $x\in A$が成り立つ.
\item $\PPP{x}$を満たすときに限り, $x\in A$が成り立つ.
\item $\PPP{x}$が成り立つときに限り, $x\in A$が成り立つ.
